---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

# btabler

`r badger::badge_custom("dev version", as.character(packageVersion("btabler")), "blue", "https://github.com/CTU-Bern/btabler")`
[![R-CMD-fullcheck](https://github.com/CTU-Bern/btabler/actions/workflows/R-CMD-full.yaml/badge.svg)](https://github.com/CTU-Bern/btabler/actions/workflows/R-CMD-full.yaml)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.path = "man/figures/README-")
```

## Example usage 

### Installing the package

The package can be installed from [github](https://github.com/CTU-Bern/btabler) via the `remotes` package

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("CTU-Bern/btabler")
```

Note that `remotes` treats any warnings (e.g. that a certain package was built under a different version of R) as errors. If you see such an error, run the following line and try again:

```{r remotes-error, eval = FALSE}
Sys.setenv(R_REMOTES_NO_ERRORS_FROM_WARNINGS = "true")
```

### Using the package 
Load it as usual:
```{r, message=FALSE}
library(btabler)
```

Create your tables via whatever means and pass them to the `btable` function:
```{r pressure, echo=FALSE}
df<-data.frame(name=c("","Row 1","Row2"),out_t=c("Total","t1","t1"),
    out_1=c("Group 1","g11","g12"),out_2=c("Group 2","g21","g22"))
btable(df,nhead=1,nfoot=0,caption="Table1")
```
`btable` returns the latex code for the table you passed.

Alignement can be changed via the `aligntot` argument:
```{r}
btable(df,nhead=1,nfoot=0,caption="Table1",aligntot="llll")
```

Where there are multiple header lines, the `nhead` argument can be used and any neighboring cells in those first rows will be merged. 
```{r}
df<-data.frame(name=c("","","Row 1","Row2"),out_t=c("Total","mean (sd)","t1","t1"),
    out_1=c("Group 1","mean (sd)","g11","g12"),out_2=c("Group 2","mean (sd)","g21","g22"))
btable(df,nhead=2,nfoot=0,caption="Table1")
```
`btable` italicizes the second row of the header by default. This can be changed via the `head_it` argument:
```{r}
btable(df,nhead=2,nfoot=0,caption="Table1",head_it=NA)
```
Likewise, aggregation of the header can also be turned of
```{r}
btable(df,nhead=2,nfoot=0,caption="Table1",head_it=NA,aggregate=FALSE)
```
Footers can also be added
```{r}
df<-data.frame(name=c("","Row 1","Row2","*Footer"),out_t=c("Total","t1","t1",""),
    out_1=c("Group 1","g11","g12",""),out_2=c("Group 2","g21","g22",""))
btable(df,nhead=1,nfoot=1,caption="Table1")
```

